%
\section{Discussion}
\label{sec:discussion}
%
The results show that Submariner has minimal impact on CPU and memory utilization, supporting its use in migration scenarios.
Database replication, on the other hand, caused more significant spikes in resource usage.
This is expected because replication requires additional resources to transfer large amounts of data and ensure data consistency.
However, it is important to consider clusters with higher idle loads, as the replication process could potentially overload such clusters.
Response time differences are minor for this use case and can be considered unimportant.
This might be interesting for clients that don't handle dynamic IP changes.
As a result, they will use the reverse proxy until they are manually set to the IP of the target cluster.
The time it takes to set the IP would likely affect the response time.
% TODO: Quelle, dass 98% gut genug sind?
An availability rate above 98\% confirms that the tool is suitable for a migration use case. 
The duration of the downtime shouldn't be influenced by the size of the database. 
Most likely the application startup times affect the downtime, because at boot up the target database must be ready for write operations.

The proposed experiment and the obtained results underlie a few limitations.
Firstly, not all types of data were considered during the migration.
% (\url{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=984278})
No user context or session data, such as a Redis store, was included in the test application.
The evaluation was also limited to a SQL database managed by an operator.
This only cover a small portion of use cases.
This is a proof of concept and we are only showing general applicability.
Finally we also have threats to validity in our experimental setup.
We made assumptions about application startup and network stability what could impact the results.